### 2007-01-15 Documentation/Paper2/paper2.tex
*** empty log message ***

\section{\AEDL\ changes and new experiment prototypes}

TABLE FROM MANUAL?

\bi
\item 
 Built-in $\beta$-beam fluxes
\item
 New AEDL features
\item
 New AEDL files in standard GLoBES delivery + changes to existing ones
\ei

Beta beams paper!

\section{New platform and interpreter support, new ways to improve the performance}

>>>>

\section{\AEDL\ changes and experiment prototypes}

\begin{table}[t!]
{\small
\begin{center}
\begin{tabular}{llp{7.0cm}c}
\hline
Experiment & Filename & Short description &  \Refs \\
\hline 
\multicolumn{4}{l}{\underline{Superbeam experiments:}} \\
T2K & {\tt T2K.glb} & J-PARC to Super-Kamiokande &  \cite{Itow:2001ee,Huber:2002mx} \\
T2HK & {\tt T2HK.glb} & J-PARC to Hyper-Kamiokande &  \cite{Itow:2001ee,Huber:2002mx} \\
NO$\nu$A & {\tt NOvA.glb} & Fermilab NuMI beamline off-axis  & \cite{Ambats:2004js,Yang_2004} \\
SPL & {\tt SPL.glb} & CERN to Fr\'{e}jus & \cite{Campagne:2006yx,Campagne:2004wt,Mezzetto:2003mm} \\[0.2cm]
\multicolumn{4}{l}{\underline{Reactor experiments:}} \\
{\sc Reactor-I} & {\tt Reactor1.glb} & Small reactor exp., 
$\mathcal{L} = 400 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$
& \cite{Huber:2003pm} \\
{\sc Reactor-II} & {\tt Reactor2.glb} & Large reactor exp., 
$\mathcal{L} = 8\, 000 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$ 
& \cite{Huber:2003pm} \\
Double{\sc Chooz} & {\tt D-Chooz\_near.glb} & Double Chooz near 
detector & \cite{Huber:2006vr} \\ 
 & {\tt D-Chooz\_far.glb} & Double Chooz far detector & \\[0.2cm]
\multicolumn{4}{l}{\underline{$\beta$-Beams:}} \\
Low $\gamma$ & {\tt BB\_100.glb} & $\gamma=100$ CERN to Fr\'{e}jus 
scenario & \cite{Campagne:2006yx} \\
Medium $\gamma$ & {\tt BB\_350.glb} & $\gamma=350$ green field scenario 
& \cite{Burguet-Castell:2005pa} \\
Variable $\gamma$ & {\tt BBvar\_WC.glb} & Variable $\gamma$ beta beam with water Cherenkov detector, $50 \lesssim \gamma \lesssim 500$ & \cite{Huber:2005jk} \\[0.2cm]
	& {\tt BBvar\_TASD.glb} & Variable $\gamma$ beta beam with totally active scint. detector (TASD), 
$100 \lesssim \gamma \lesssim 3\, 000$ & \cite{Huber:2005jk} \\[0.4cm]
\multicolumn{4}{l}{\underline{Neutrino factories:}} \\
Standard & {\tt NFstandard.glb} & Standard neutrino factory, $50 \, \mathrm{kt}$ magnetized iron calorimeter, 
$E_\mu = 50 \, \mathrm{GeV}$ & \cite{Huber:2002mx} \\
Variable $E_\mu$ & {\tt NFvar.glb} & Variable neutrino factory, disapp. channels
{\em without} CID; $10 \, \mathrm{GeV} \lesssim E_\mu \lesssim 80 \, \mathrm{GeV}$ & \cite{Huber:2002mx,Huber:2006wb}  \\
Gold + Silver & {\tt NF\_GoldSilver.glb} & As {\tt NFvar.glb} 
plus 5~kt ECC detector for Silver Channel
measurement & \cite{Huber:2002mx,Huber:2006wb,Autiero:2003fu} \\
Hybrid detector & {\tt NF\_hR\_lT.glb} & As {\tt NFvar.glb}, but 
lower threshold and better energy resolution & \cite{Huber:2002mx,Huber:2006wb} \\
\hline
\end{tabular}
\end{center}
} % small
\mycaption{\label{tab:experiments} 
Pre-defined experiment prototypes coming with \GLOBESN : The columns represent the \AEDL\ filename, 
a short description, and the references in which they are originally used and 
discussed (except from minor modifications, such as a different implementation of 
the energy threshold function). 
%
IS THE GAMMA=350 OPTION REALLY GREEN-FIELD? I THOUGHT THAT THIS MAY BE THE MAXIMUM
ONE COULD GET OUT OF THE SPS WITH ACCELERATOR MODIFICATIONS? [WW]
}
\end{table}

\AEDL\ (Abstract Experiment Definition Language) is a special syntax developed for the description of
experiments in \GLOBES\ represented by simple text files. Core part of \AEDL\ are the following constructions
(for details, see \Ref~\cite{Manual}):
\begin{description}
\item[Channel] A channel represents an oscillation channel from the source flux, over the initial and final
flavors and the use of neutrinos or antineutrinos, to the interaction type and cross section. The result
is an event rate vector.
\item[Rule] A rule combines one or more signal channels with one or more background channels. The rates
from these channels are added, and the signal and background are implemented with specific systematics, \ie,
systematics is connected to the concept of a rule.
The result of a rule is a systematics $\chi^2$ corresponding to \equ{chipull}.
\item[Experiment] An experiment is a combination of one or more rules, which may correspond to different
appearance and disappearance channels, neutrino and antineutrino operations modes, \etc. An experiment has a common detector and baseline, but may use more different fluxes (such as for neutrinos and antineutrinos). Therefore,
the matter density profile is the same for all rules of an experiment. The result of an experiment
is again a systematics $\chi^2$, but summed over all rules.
\item[Experiment combination] An experiment combination consists of different experiments with different detectors, baselines, and (uncorreleted) matter density profiles. The result of an experiment combination
is again a systematics $\chi^2$, but summed over all experiments.
\end{description}
Note that after the $\chi^2$ is summed over all rules or experiments as specified by the user in the application software, \equ{margin} is applied, and the oscillation parameters are marginalized over.

In \GLOBESN , this construction of experiments is extended by user-defined systematics, which allows
the user to break up the strict coupling of systematics with rules. For example, systematics can be
correlated between different rules or experiments, such as for an reactor experiment with identical
near and far detectors. In addition, one can introduce user-defined systematical errors.
For that purpose, the former error dimension concept has been changed and
extended. For example, one has to give each user-defined systematics a name, and this name has
to be matched by the application software. 
%
Further changes in \AEDL\ are the requirement of a minimum \GLOBES\ version the \AEDL\ is running with,
and the extension of lists as \AEDL\ variables and an interpolation feature.

As far as the experiment prototypes are concerned, a list of the ones provided with \GLOBESN\ 
is given in \Tab~\ref{tab:experiments}. These prototypes can be modified for the definition of
one's own experiments (experimentalist), or they can be used for the test of new physics concepts
(phenomenologist/theorist).
Note that some of these experiments may contain 
integrated luminosities, baseline, fluxes, efficiencies, or other factors, which the user
may not agree with and which can be easily adjusted. Some of the \AEDL\ files have been
changed or updated from eariler versions, such as for T2K and T2HK, or the standard neutrino
factory. Other files represent the results from recent developments, such as the variable energy
beta beam or neutrino factory files. They push \AEDL\ to the edge in terms of advanced features,
such as variable bin widths, use of the new interpolation feature, threshold function implementations, \etc.
In particular, note that Double Chooz requires user-defined
systematics, and the beta beams built-in beta beam fluxes. Both of these features are only
available in \GLOBESN\ and higher. Some of the files require that \AEDL\ variables be pre-set by the
user, such as the muon energy for the variable energy neutrino factory. These variables are
described in the corresponding file headers. Old \AEDL\ prototypes should still run, but will not
be maintained by the \GLOBES\ team anymore.

\section{Internal changes and improved performance}

New platform and interpreter support, new ways to improve the performance
